%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[./fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
\definecolor{darktext}{HTML}{000000}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Yahya}{Kayani}
\position{Software Engineer}
\address{}

\mobile{(+1) 902-902-1858}
\email{yahya.kayani@dal.ca }
\homepage{yahyakiani.github.io/reactJs-resume-template/}
\github{Yahyakiani}
\linkedin{yahya-kayani}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

\quote{}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Vergo.AI}
  {}
% The date on the letter, default is the date of compilation
% \letterdate{}
% The title of the letter
\lettertitle{Job Application for Student Programmer}
% How the letter is opened
% \letteropening{Dear Mr./Ms. Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Yahya Kayani~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a MCS pursuing my Master's degree in Computer Science at Dalhousie University, and I have previously worked 
as a Software Engineer developing web applications using technologies such as ReactJS, Flask, and NodeJS.I am proficient in using technologies such as ReactJS, Flask, and NodeJS to build web applications. 
My expertise also includes working with WebApp ReactJS, MaterialUI, Servernode JS/Express, Google Firebase functions, 
MongoDB, libraries such as SocketIO and ReactJS.I have excellent coding skills and maintain proper coding practices and documentation, even under tight deadlines.

\lettersection{Why Hamza.AI?}
I am thrilled about the opportunity to collaborate with HCI4Good and your industry partner, Vergo.AI. The focus on Computer Vision and Machine Learning 
techniques aligns perfectly with my interests. I am confident that my technical skills and  experience align with the job 
requirements and can help drive the project forward.

\lettersection{Why Me?}
My background as a Software Engineer, along with my education in Computer Science, has allowed me to attain a strong foundation
of technical skills specifically in Modern Javascript and python frameworks such as openCV. Moreover, I built and deployed automation bots using selenium and developed web-crawlers 
for data extraction and analysis. I also implemented a RESTful API server for communication between frontend and the backend.
Currently, I am researching comparative bias analysis in large transformer models in NLP using machine learning techniques, and I am eager to apply my skills and knowledge 
to real-world projects. I am confident that I can contribute significantly to your project and help drive it forward to success.

Thank you for your consideration.


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
