%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Nmx Global Software} % Organization
    {} % Location
    {Jan. 2019 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced database performance by optimizing relational databases and implementing efficient queries, reducing application breakdowns by 15\% through ORM techniques.}
        \item {Architected and implemented dashboards to give members a more comprehensive insight into their working.}
        \item {Increased system efficiency by developing API microservices in Node.js and Python, utilizing ORM, resulting in a 20\% increase in processing speed.}
        \item {Contributed to Project (Limesurvey) by resolving 30+ critical bugs and introducing new features, thereby advancing project functionality and user satisfaction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python Developer} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and deployed automation bots utilizing selenium focusing on ease of use, flexibility, and scaling.}
        \item {Developed efficient web-crawlers for data extraction from various websites using lxml and BeautifulSoup for analysis.}
        \item {Implemented RESTful API server using Swagger UI for communication between frontend and the backend. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
