%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}



  \cventry
  {Core Developer} % Affiliation/role
  {Neural Edge } % Organization/group
  {Python, SQLalchemy, PostgreSQL, ReactJs, Redux} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Worked on a predictive modeling project for a healthcare organization to optimize patient allocation and resource utilization.}
      \item {Utilized statistical analysis techniques and optimization algorithms to develop a predictive model for patient demand forecasting.}
      \item {Implemented application interaction with server side using JSON parsing.Performed Database ORM Query Optimizations.}
      \item { Improved resource allocation efficiency by 15\%, resulting in reduced wait times for patients and increased overall satisfaction.}
    \end{cvitems}
  }

   
  %---------------------------------------------------------
  \cventry
  {Full-stack Developer} % Affiliation/role
  {Heartbeat} % Organization/group
  {React, Node.js, RabbitMQ, NestJS} % Location
  {} % Date(s)
  {
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Spearheaded the development and implementation of an extensive CRM tool aimed at streamlining the entire house construction/acquisition process, from design to homeowner management.}
    \item {Designed and executed dashboard enhancements to improve data flow efficiency, along with integrating new features such as time-off synchronization scripts, significantly enhancing operational workflows.}
    \item {Implemented an ICS feed integration, enabling the Sales team to subscribe to various event types on Outlook and Google Calendars, thereby optimizing communication and scheduling processes.}
    \item {Led the resolution of critical bug cases and the implementation of email synchronization from a local database to Outlook through API, enhancing the reliability of the system.}
    \item {Developed and optimized backend ORM, improving system performance and scalability. Additionally, worked on notification system enhancements to support new user types, ensuring a seamless user experience across the platform.}
  \end{cvitems}
}

  
  %---------------------------------------------------------
  \cventry
  {Creator and Developer} % Affiliation/role
  {Colorblind Mode Chrome Extension} % Organization/group
  {Javascript, Chrome Extension APIs} % Location
  {April 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Designed and developed the Colorblind Mode Chrome Extension, an open-source project aimed at making the internet more accessible to people with color blindness.}
      \item {Implemented a color matrix algorithm that modifies the colors on web pages based on the selected colorblindness profile (Protanopia, Deuteranopia, or Tritanopia).}
      \item {Enabled developers to test the accessibility of their websites by allowing them to view their content as someone with color blindness would see it.}
      \item {Continuously improved the extension to ensure it is user-friendly, easy to use with the latest versions of Google Chrome.}
    \end{cvitems}
  }
%---------------------------------------------------------
  % \cventry
  %   {Core Developer} % Affiliation/role
  %   {Neural Edge } % Organization/group
  %   {Python, SQLalchemy, PostgreSQL} % Location
  %   {} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Worked on a predictive modeling project for a healthcare organization to optimize patient allocation and resource utilization.}
  %       \item {Utilized statistical analysis techniques and optimization algorithms to develop a predictive model for patient demand forecasting.}
  %       \item {Implemented application interaction with server side using JSON parsing.Performed Database ORM Query Optimizations.}
  %       \item { Improved resource allocation efficiency by 15\%, resulting in reduced wait times for patients and increased overall satisfaction.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Core Project Member (Final Year Project)} % Affiliation/role
    {Real-Time Point of Interest Detection System} % Organization/group
    {Python, Tensorflow, Kivy Framework, openCV, Raspberry PI} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed in python using Kivy Framework for Cross-Platform UI development along with TensorFlow
        Framework for Model Training, Optimization and testing.}
        \item {It performed monitoring and analysis on a set of Image frames. A Vision Based Security system.It relied on
        3 layers of security which are human detection, Face detection, and Gait detection.}
        \item {Gait detection was applied using Recurrent neural networks. Made use of Transfer Learning Technique for
        our Deep learning Model.}
        \item {Awarded 2nd Position in Open House Competition held in COMSAT University Islamabad.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Core DEVELOPER} % Affiliation/role
  %   {Tweet Sentiment Analyser Bot} % Organization/group
  %   {NLTK, MatPlotlib, Pandas, NumPy} % Location
  %   {} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Used NLP (NLTK Library) concepts like tokenization, stemming and bag of words in python to prepare the data to be fed to the bot for training.} 
  %       \item {Trained the chatbot using deep learning concepts like Feed Forward Neural Net with linear layers and ReLu activation function.} 
  %       \item {Improved the accuracy of the bot by adding dropout layers and implemented early stopping.}
  %       \item {Used PyTorch, NumPy, Pandas to write the code and Matplotlib to show the accuracy of the bot. Used Jupyter Notebook to write the code, analyze data and manipulate data to feed to the bot.}
  %       % \item {A Cloud application built in React/Typescript for maintainence and provision of Cloud Services to numerous clients.}
  %       % \item {To maintain the existing code base to standards determined by the Project Manager, by performing optimizations and reworks.}
  %       % \item {Assist in the development and creation of new application team initiatives.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
% \cventry



%---------------------------------------------------------
\end{cventries}
